Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex
Section 5 polishing / comments

\newcommand{\FINISH}[3]{\ifdraft\textcolor{#1}{[#2: #3]}\fi}
\newcommand{\bcp}[1]{\FINISH{dkred}{B}{#1}}
\newcommand{\BCP}[1]{\FINISH{dkred}{B}{\bf #1}}
\newcommand{\afm}[1]{\FINISH{dkgreen}{A}{#1}}
\newcommand{\dpw}[1]{\FINISH{dkblue}{D}{#1}} % Toronto Maple Leafs Blue :-)
\newcommand{\saz}[1]{\FINISH{orange}{SZ}{#1}}
\newcommand{\ksf}[1]{\FINISH{teal}{K}{#1}}
\newcommand{\sam}[1]{\FINISH{dkpurple}{SM}{#1}}

@@

For the\bcp{why ``the''?  Are we talking about some set of QRE examples
  already?} QRE examples, the $x_i$'s are in $W(c_1)$ and the $y_i$'s are 
in $W(c_2)$, so we can construct ${x'_i} = \canonizer(c_1)(x_i)$ in $K(c_1)$
and ${y'_i} = \canonizer(c_2)(y_i)$ is in $K(c_2)$. To synthesize the
desired quotient lens $q: c_1 \Leftrightarrow c_2$ that is consistent with the
input-output examples $\{(x_1, y_1), \ldots, (x_n, y_n)\}$ it suffices to
synthesize a bijective lens $\ell : K(c_1) \Leftrightarrow K(c_2)$ that is
consistent with the canonized examples $\{({x'_1}, {y'_1}), \ldots, ({x'_n},
{y'_n})\}$ and then apply the canonizers at the outside. Our procedure for QRE
lens synthesis is thus
\begin{enumerate}
  \item
  Compute $K(c_1)$, $K(c_2)$,
  \item
  Compute $\{({x'_1}, {y'_1}), \ldots, ({x'_n}, {y'_n})\}$ where ${x'_i} =
  \canonizer(c_1)(x_i)$ and ${y'_i} = \canonizer(c_2)(y_i)$,
\item Synthesize, using Optician's algorithm, a bijective lens
  $\ell : K(c_1) \Leftrightarrow K(c_2)$ that is consistent with the examples
  $\{({x'_1}, {y'_1}),\allowbreak \ldots,\allowbreak ({x'_n}, {y'_n})\}$
  \item
  Return $q = \kw{rquot}(\kw{lquot}(c_1, \ell), c_2) : c_1 \Leftrightarrow
  c_2$ \bcp{punctuate this enumeration as if it were running text: ``, and''
  at the end of (3) and period here.}
\end{enumerate}

\saz{Do we want to state formally the completeness of this algorithm?}

@@

In this case, one example is sufficient to uniquely determine the desired
transformation.\saz{Is that true?}

\saz{We might want to say something more precise about the running time or
  expected performance of this algorithm, perhaps to set up the evaluation
  section.  Something along the lines of: ``Although the algorithm is complete
  in theory, in the worst case, it may take an unbounded [???IS THIS CORRECT?]
  amount time to search for a satisfactory lens.  Nevertheless, this algorithm
  performs well in practice on numerous examples, as we show in the next
  section.}

>>>>

\newcommand{\FINISH}[3]{\ifdraft\textcolor{#1}{[#2: #3]}\fi}
\newcommand{\bcp}[1]{\FINISH{dkred}{B}{#1}}
\newcommand{\BCP}[1]{\FINISH{dkred}{B}{\bf #1}}
\newcommand{\afm}[1]{\FINISH{dkgreen}{A}{#1}}
\newcommand{\dpw}[1]{\FINISH{dkblue}{D}{#1}} % Toronto Maple Leafs Blue :-)
\newcommand{\saz}[1]{\FINISH{orange}{SZ}{#1}}
\newcommand{\SAZ}[1]{\FINISH{orange}{SZ}{\bf #1}}
\newcommand{\ksf}[1]{\FINISH{teal}{K}{#1}}
\newcommand{\sam}[1]{\FINISH{dkpurple}{SM}{#1}}

@@

For the\bcp{why ``the''?  Are we talking about some set of QRE examples
  already?} QRE examples, the $x_i$'s are in $W(c_1)$ and the $y_i$'s are 
in $W(c_2)$, so we can construct ${x'_i} = \canonizer(c_1)(x_i)$ in $K(c_1)$
and ${y'_i} = \canonizer(c_2)(y_i)$ is in $K(c_2)$. To synthesize the
desired quotient lens $q: c_1 \Leftrightarrow c_2$ that is consistent with the
input-output examples $\{(x_1, y_1), \ldots, (x_n, y_n)\}$ it suffices to
synthesize a bijective lens $\ell : K(c_1) \Leftrightarrow K(c_2)$ that is
consistent with the canonized examples $\{({x'_1}, {y'_1}), \ldots, ({x'_n},
{y'_n})\}$ and then apply the canonizers at the outside. Our procedure for QRE
lens synthesis is thus
\begin{enumerate}
  \item
  Compute $K(c_1)$, $K(c_2)$,
  \item
  Compute $\{({x'_1}, {y'_1}), \ldots, ({x'_n}, {y'_n})\}$ where ${x'_i} =
  \canonizer(c_1)(x_i)$ and ${y'_i} = \canonizer(c_2)(y_i)$,
\item Synthesize, using Optician's algorithm, a bijective lens
  $\ell : K(c_1) \Leftrightarrow K(c_2)$ that is consistent with the examples
  $\{({x'_1}, {y'_1}),\allowbreak \ldots,\allowbreak ({x'_n}, {y'_n})\}$
  \item
  Return $q = \kw{rquot}(\kw{lquot}(c_1, \ell), c_2) : c_1 \Leftrightarrow
  c_2$ \bcp{punctuate this enumeration as if it were running text: ``, and''
  at the end of (3) and period here.  And lowercase letters at the
  beginnings of the items.}
\end{enumerate}

\saz{Do we want to state formally the completeness of this algorithm?}\BCP{+1}

@@

In this case, one example is sufficient to uniquely determine the desired
transformation.\SAZ{Is that true?}\BCP{Seems more likely that the desired
  transformation happened to be the first one that the synthesis algorithm
  reached.  Indeed, my intuition is that {\em every} synthesis problem with
  a finite set of examples has infinitely many solutions.  Is that right?}

\SAZ{We might want to say something more precise about the running time or
  expected performance of this algorithm, perhaps to set up the evaluation
  section.  Something along the lines of: ``Although the algorithm is complete
  in theory, in the worst case, it may take an unbounded [???IS THIS
  CORRECT?]\bcp{Surely it's bounded by some exponential formula involving the
    size of the inputs...?} 
  amount time to search for a satisfactory lens.  Nevertheless, this algorithm
  performs well in practice on numerous examples, as we show in the next
  section.}
